### 2019-06-28 ThesisJo/2_publications.tex
2019-06-27

We present four journal-papers concerned with the \emph{adaptive} and \emph{hardware accelerated} formation of acoustic images: the first three reconstructs them from acoustic echoes, and the last synthesizes them through acoustic simulation.

@@

We relax MVDR through a combination of temporal and spatial averaging, and regularization. This makes it robust and produces images with slightly more details and less noise than delay-and-sum. The resulting solution space is still continuous, but tighter bounded.

We find that implementing MVDR on GPUs instead of CPUs accelerates it by two orders of magnitude, but requires considerable and delicate efforts to reduce arithmetic operations and fine-tune cache usage. The design is limited to 32 channels due data dependencies that are complicated and not inherently parallel, combined with the relatively limited bandwidth of this hardware architecture.

@@

This article describes an acoustic simulator for SAS, implemented on GPUs using OpenGL and OpenCL. Its purpose is to enable AUVs to compare its images on-the-fly to simulations of various known objects, for more responsive, accurate and flexible automatic target recognition (ATR).

@@

We discuss the design in-depth using a new navigational notation system, extended with topological concepts from robotics and homogeneous coordinates. We find it incredibly helpful for keeping track of complex geometries, numerical representations and higher level abstractions such as manipulating rigid objects.

>>>>

We present four journal published papers concerned with \emph{adaptive} and \emph{hardware accelerated} formation of acoustic images: the first three reconstruct them from acoustic echoes and the last synthesizes them through acoustic simulation.

@@

We relax MVDR through a combination of temporal and spatial averaging, and regularization. This makes it robust and produces images with slightly more details and less noise than delay-and-sum. The resulting solution space is still continuous, but more tightly bound.

We find that implementing MVDR on GPUs instead of CPUs accelerates it by two orders of magnitude, but requires considerable and delicate efforts to reduce arithmetic operations and fine-tune cache usage. The design is limited to 32 channels due to data dependencies that are complicated and not inherently parallel, combined with the relatively limited bandwidth of this hardware architecture.

@@

This article describes an acoustic simulator for SAS, implemented on GPUs using OpenGL and OpenCL. It enables AUVs to compare its images on-the-fly to simulations of various known objects, for more responsive, accurate and flexible automatic target recognition (ATR).

@@

The design is discussed in-depth using a new navigational notation system, extended with topological concepts from robotics and homogeneous coordinates. We find it incredibly helpful for keeping track of complex geometries, numerical representations and higher level abstractions such as manipulating rigid objects.

### 2019-06-28 ThesisJo/frontmatter.tex
2019-06-26
2019-06-27

@@

\begin{markdown}
Hey
\end{markdown}

\chapter*{Preface}
% \cfoot{\thepage}

@@

@@

\newpage
\chapter*{List of Publications}

@@

%\newpage
\chapter*{Related Publications}

>>>>

\cleardoublepage

\vspace*{\fill}
\begin{center}
{\huge\bf Til Joakim} \\[1.5cm]
{\Large aldri gi opp}
\end{center}
\vspace*{\fill}

\clearpage

@@

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
% \cfoot{\thepage}

@@

This journey seems to have started a different life ago. Along the way more appreciation has piled up in the depths of my heart than I believed possible. I can only hope to give a little back by extending my sincerest gratitude to

\emph{Professor Andreas Austeng}, for offering great advice, insights, ever-presence, persistence and unwaivering optimism---simply being the best supervisor imaginable;

\emph{Jon Petter Åsen}, for being a wonderful and joyful office mate, colleague, coauthor and friend during the first years;

\emph{Cherie}, my dear faraway friend, for the steady stream of encouraging thoughts, patience and help---asking nothing in return;

\emph{the Department of Informatics, IFE}, for initially granting me this opportunity and later extending it;

\emph{the Norwegian Defence Research Institute, FFI}, for providing data to study and being an amazing workplace;

\emph{Professor Roy Hansen} (FFI/IFE), for initially sparking my interest for sonars and this PhD;

\emph{Professor Sverre Holm} (FFI/IFE), for being my second supervisor, an inspiration, a bottomless pit of knowledge and an aid while I lectured signal processing;

\emph{Stig Synnes} (FFI/IFE), for getting me into volleyball and the mutual friendly nudges to finish writing;

\emph{Kenneth Gade} (FFI), for volleyball enthusiasm and the inspiration and help developing the notation in paper IV,

\emph{Carl-Inge C. Nielsen} (IFE), for the time, knowledge and flying start you offered when this all began;

\emph{Herman Midelfart (FFI)}, for getting a chance to work with you before your days were numbered;

\emph{other colleagues and students} at IFE and FFI, for making work and life enjoyable, every day;

\emph{Friskvernklinikken}, Asker, for showing me a path where I thought there were none;

\emph{Marthe Arnesen}, for the gesture you once made yourself, for what is and for what may come;

\emph{my family}, for all your support, love and presence---through good and bad;

(\emph{myself}, I could not have done it without you;)

\emph{Joakim}, for giving me purpose, perspective and joy. This is for you.

@@

\textit{Cognition:}\\The mental action or process or acquiring knowledge and understanding through thought, experience, and the senses.

\newpage
\chapter*{Included publications}
\addcontentsline{toc}{chapter}{Included publications}

@@

%\newpage
\chapter*{Excluded Publications}
\addcontentsline{toc}{chapter}{Excluded publications}
